---
title: "Week 4 Quiz"
author: "Santiago Fernández"
date: "May 28, 2019"
output: html_document
---

## Question 1

A pharmaceutical company is interested in testing a potential blood pressure lowering medication. Their first examination considers only subjects that received the medication at baseline then two weeks later. The data are as follows (SBP in mmHg)

Subject	Baseline	Week 2
1	140	        132
2	138	        135
3	150	        151
4	148	        146
5	135	        130

Consider testing the hypothesis that there was a mean reduction in blood pressure? Give the P-value for the associated two sided T test.

(Hint, consider that the observations are paired.)


- 0.05
- 0.10
- 0.087
- 0.043

```{r}
Baseline <- c(140,138,150,148,135)
Week2 <- c(132,135,151,146,130)
t.test(Baseline,Week2,alternative ="two.sided", paired = TRUE)

```


**Answer is 0.087**



## Question 2

A sample of 9 men yielded a sample average brain volume of 1,100cc and standard deviation of 30cc. What is the complete set of values of μ0 that a test of H0:μ=μ0 would fail to reject the null hypothesis in a two-sided 5% Students t-test ?

- 1031 to 1169
- 1080 to 1120
- 1081 to 1119
- 1077 to 1123

```{r}
CI <- 1100 + c(-1,1)*qt(0.975,(9-1))*30/sqrt(9)
CI
```

**Answer is 1077 to 1123**



## Question 3

Researchers conducted a blind taste test of Coke versus Pepsi. Each of four people was asked which of two blinded drinks given in random order that they preferred. The data was such that 3 of the 4 people chose Coke. Assuming that this sample is representative, report a P-value for a test of the hypothesis that Coke is preferred to Pepsi using a one sided exact test.

- 0.31
- 0.62
- 0.005
- 0.10

For binomial data, one way to compare two groups is using a Chi-square test.

```{r}
chisq.test(c(3,1),p=c(.5,.5))
```
**Answer is 0.31**



## Question 4

Infection rates at a hospital above 1 infection per 100 person days at risk are believed to be too high and are used as a benchmark. A hospital that had previously been above the benchmark recently had 10 infections over the last 1,787 person days at risk. About what is the one sided P-value for the relevant test of whether the hospital is *below* the standard?

- 0.03
- 0.52
- 0.22
- 0.11

```{r}
lambda <- 1/100
t <- 1787
ppois(10,lambda*t)
```

**Answer is 0.03**
