---
title: "Week 3 Quiz"
author: "Santiago Fernández"
date: "May 21, 2019"
output: html_document
---
## Question 1

In a population of interest, a sample of 9 men yielded a sample average brain volume of 1,100cc and a standard deviation of 30cc. What is a 95% Student's T confidence interval for the mean brain volume in this new population?

- [1031, 1169]
- [1080, 1120]
- [1092, 1108]
- [1077,1123]

```{r}
mn = 1100
s = 30
n = 9

round(mn + c(-1,1)*qt(.975, df = 8)*s/sqrt(n))

```

**Correct answer is [1077,1123]**



## Question 2

A diet pill is given to 9 subjects over six weeks. The average difference in weight (follow up - baseline) is -2 pounds. What would the standard deviation of the difference in weight have to be for the upper endpoint of the 95% T confidence interval to touch 0?

- 2.10
- 0.30
- 1.50
- 2.60

```{r}
mn = -2
s = s
n = 9

#-2 +qt(.975, df=8)*s/sqrt(n) = 0 
s = 2/qt(.975, df=8)*sqrt(n)
print(round(s,2))
```

**Correct answer is 2.60**



## Question 3

In an effort to improve running performance, 5 runners were either given a protein supplement or placebo. Then, after a suitable washout period, they were given the opposite treatment. Their mile times were recorded under both the treatment and placebo, yielding 10 measurements with 2 per subject. The researchers intend to use a T test and interval to investigate the treatment. Should they use a paired or independent group T test and interval?

- Independent groups, since all subjects were seen under both systems
- It's necessary to use both
- A paired interval
- You could use either

Answer: A paired interval would be better, we are looking at the same runner in two different times.

**Correct answer is A paired interval**



## Question 4

In a study of emergency room waiting times, investigators consider a new and the standard triage systems. To test the systems, administrators selected 20 nights and randomly assigned the new triage system to be used on 10 nights and the standard system on the remaining 10 nights. They calculated the nightly median waiting time (MWT) to see a physician. The average MWT for the new system was 3 hours with a variance of 0.60 while the average MWT for the old system was 5 hours with a variance of 0.68. Consider the 95% confidence interval estimate for the differences of the mean MWT associated with the new system. Assume a constant variance. What is the interval? Subtract in this order (New System - Old System).

- [-2,70, -1.29]
- [1.29, 2.70]
- [1.25, 2.75]
- [-2.75, -1.25]

```{r}
mns = 3
sns = .60
mos = 5
sos = .68
nns = 10
nos = 10

(mns - mos) + c(-1,1)*qt(.975,10+10-2)*sqrt(((10-1)*sns+(10-1)*sos)/(10+10-2))*sqrt((1/10)+(1/10))
```

**Correct answer is [-2.75,-1.25]**



## Question 5

Suppose that you create a 95% T confidence interval. You then create a 90% interval using the same data. What can be said about the 90% interval with respect to the 95% interval?

- It is impossible to tell.
- The interval will be wider
- The interval will be the same width, but shifted.
- The interval will be narrower.

The interval will be narrower, we sacrifice confidence to gain precision.

**Correct answer is The interval will be narrower**



## Question 6

To further test the hospital triage system, administrators selected 200 nights and randomly assigned a new triage system to be used on 100 nights and a standard system on the remaining 100 nights. They calculated the nightly median waiting time (MWT) to see a physician. The average MWT for the new system was 4 hours with a standard deviation of 0.5 hours while the average MWT for the old system was 6 hours with a standard deviation of 2 hours. Consider the hypothesis of a decrease in the mean MWT associated with the new treatment.

What does the 95% independent group confidence interval with unequal variances suggest vis a vis this hypothesis? (Because there's so many observations per group, just use the Z quantile instead of the T.)

- When subtracting (old - new) the interval is entirely above zero. The new system does not appear to be effective.
- When subtracting (old - new) the interval is entirely above zero. The new system appears to be effective.
- When subtracting (old - new) the interval contains 0. There is not evidence suggesting that the new system is effective.
- When subtracting (old - new) the interval contains 0. The new system appears to be effective.

